SylvanSeeds, a seed germination database for temperate deciduous forests

### 2020-10-12 README.Rmd
corrected references
zenodo doi

@@

> Fernández-Pascual, E. (2020). [SylvanSeeds, a seed germination database for temperate deciduous forests.](https://doi.org/10.1111/jvs.12960) *Journal of Vegetation Science*

>>>>

[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.4081377.svg)](https://doi.org/10.5281/zenodo.4081377)

@@

> Fernández-Pascual, E. (2020). [SylvanSeeds, a seed germination database for temperate deciduous forests.](https://doi.org/10.1111/jvs.12960) *Journal of Vegetation Science.*

### 2020-10-12 doc/manuscript.Rmd
zenodo doi

```{r fig1, echo = FALSE, message = FALSE, warning = FALSE, fig.pos = "H", fig.cap = "**Figure 1** *Geographical distribution of the germination records in the database. Each golden circle is a record. The green areas correspond to the extension of the Temperate Broadleaf and Mixed Forests biome according to the *WWF*.*", fig.width=7, fig.height=3}
knitr::include_graphics("../results/Fig1.png")
```

@@

```{r fig2, echo = FALSE, fig.pos = "H", fig.cap = "**Figure 2** *Example of the germination records as shown by the SylvanSeeds app. Records for one species, the European common beech, Fagus sylvatica. Each panel shows the results for a combination of experimental conditions, with the germination temperature varying within each panel. Bars represent the mean germination proportion and brackets the 95% binomial confidence interval.*", fig.width=7, fig.height=5}
knitr::include_graphics("../results/Fig2.png")
```

@@

All persons can use the database providing they cite this paper properly in any publications or in the metadata of any derived products that are produced using the database. The database is provided as [**Appendix S5**](https://github.com/efernandezpascual/sylvanseeds/blob/master/doc/Appendix%20S5%20-%20Database.csv) of this manuscript, but please do visit https://efernandezpascual.github.io/home/sylvanseeds.html to check for updates. It can be visualized with the *SylvanSeeds* app at  https://efernandezpascual.shinyapps.io/sylvanseeds/. The code to create this manuscript and the app is stored at https://github.com/efernandezpascual/sylvanseeds.

>>>>

```{r fig1, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "**Figure 1** *Geographical distribution of the germination records in the database. Each golden circle is a record. The green areas correspond to the extension of the Temperate Broadleaf and Mixed Forests biome according to the WWF.*", fig.width=7, fig.height=3}
knitr::include_graphics("../results/Fig1.png")
```

@@

```{r fig2, echo = FALSE, fig.cap = "**Figure 2** *Example of the germination records as shown by the SylvanSeeds app. Records for one species, the European common beech, Fagus sylvatica. Each panel shows the results for a combination of experimental conditions, with the germination temperature varying within each panel. Bars represent the mean germination proportion and brackets the 95% binomial confidence interval.*", fig.width=7, fig.height=5}
knitr::include_graphics("../results/Fig2.png")
```

@@

All persons can use the database providing they cite this paper properly in any publications or in the metadata of any derived products that are produced using the database. The database is provided as [**Appendix S5**](https://github.com/efernandezpascual/sylvanseeds/blob/master/doc/Appendix%20S5%20-%20Database.csv) of this manuscript, but please do visit https://efernandezpascual.github.io/home/sylvanseeds.html to check for updates. It can be visualized with the *SylvanSeeds* app at  https://efernandezpascual.shinyapps.io/sylvanseeds/. The code to create this manuscript and the app is stored at https://github.com/efernandezpascual/sylvanseeds. A version of record of the repository can be found at https://doi.org/10.5281/zenodo.4081377.
